---
output: html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LizzieLift

<!-- badges: start -->
<!-- badges: end -->

The goal of LizzieLift is to make the creation of lift curves with weighted and unweighted data simple. A lift curve compares the actual values of some target of a model to the predicted values of the model by ordering the data according to the predicted values, binning the data, and then comparing the mean value of the predicted and actual values in each bin. The ordering of the data ensures that the plot of the mean predicted values will be monotonically increasing, and if the model is good, the plot of the mean actual values should be as well. When a model is built using weighted data, we prefer to weight each entry in the lift curve as well. Lizzie was unable to find an easily download-able package that performed this function well, so she built a package herself to ensure the weighting was done according to her needs.

## Installation

You can install the development version of LizzieLift like so:

``` {r}
#for others:
#run devtools::install_github("easoneli176/LizzieLift") to install package

#on my personal machine
library(devtools)
library(LizzieLift)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(LizzieLift)

mock_data <- data.frame(preds=rep(1:4,10), target=rep(1:5,8), weights=rep(1:2,20))

wltable(mock_data,"preds","target","weights",3)
wlplot(mock_data,"preds","target","weights",3)
wlcredplot(mock_data,"preds","target","weights",3)
ltable(mock_data,"preds","target",3)
lplot(mock_data,"preds","target",3)

#Notes on package creation for Lizzie that probably belong in a template:
#when creating a package, use roxygen2::roxygenise() to create documentation after writing the source code .R file
#ctrl+shift+B rebuilds package after editing
#to connect existing package to github, make sure project has version control, commit changes, then run in the terminal:
#git remote add origin git@github.com:easoneli176/reponame.git (can copy this link from repo)
#git branch -M main
#git push -u origin main

#if packages need uploading:
#manually find the package in windows, they're stored here: C:\Users\eason\AppData\Local\R\win-library\4.2
#move the package out of that folder and keep it somewhere in case stuff breaks
#then install the newest version. If issues, can go to cran website and get zip file to move into folder
#The code `devtools::build_readme()` is handy for keeping README.md up to date. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
#This seems to fail without changing the output type to html, so trying that
```





